Exposure Consequences - Statistics and Figures

### 2018-01-22 ManuscriptMaterials.Rmd
make parallelization optional, depending on installed packages

---
title: "Exposure Consequences - Statistics and Figures"
output:
  pdf_document:
    number_sections: yes
  html_notebook:
    number_sections: yes
---

@@

```{r}
cat('\nCLASSIC\n\n')
getPeakConfidenceInterval('classic',part='all',CIs=c(.95))
cat('\nEXPOSURE\n\n')
getPeakConfidenceInterval('exposure',part='all',CIs=c(.95))
```

Although the two peaks are not different from each other, the 95% confidence interval for the classically trained group includes the 45 degree target (where the visual feedback was during training), whereas the 95% confidence interval for the exposure training group includes the 75 degree target (where the hand really was during training). So something might be going on -- but the evidence is far from concrete.

>>>>

---
title: "Exposure Consequences - Statistics and Figures"
output:
  html_notebook:
    number_sections: yes
  pdf_document:
    number_sections: yes
---

@@

```{r}
getPeakConfidenceInterval('classic',part='all',CIs=c(.95))
getPeakConfidenceInterval('exposure',part='all',CIs=c(.95))
```

Although the two peaks are not different from each other, the 95% confidence interval for the classically trained group includes the 45 degree target (where the visual feedback was during training) but not the 75 degree target, whereas the 95% confidence interval for the exposure training group includes the 75 degree target (where the hand really was during training) but not the 45 degree target. Something might be going on -- but the evidence is far from concrete.
